Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-06-06 ms.tex
updating model fitting results section.

@@

We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
We model the two dimensional Fourier power spectral density $f(k_{x,i}',k_{y,i}')$ for one angle $\theta_i$ as
\begin{equation}
f(k_{x,i}',k_{y,i}', a_i, b,c) = a \exp{\left(- |k_{x,i}'| / b \right)} \left( \frac{1}{(0.5 c)^2 + k_y'^2} \right),
\end{equation}
where $k_x'$ and $k_y'$ are rotated frequency coordinates in the parallel and perpendicular directions, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorentzian full width at half maximum of the perpendicular dependence.
For each of the three angles, there is a set of rotated coordinates centered at $(k_{x,0},k_{y,0})$= (0,0) following:
\begin{equation}
k_x'(\theta_i) = k_x \cos{\theta_i} + k_y \sin{\theta_i}
\end{equation}
and
\begin{equation}
k_y'(\theta_i) = -k_x  \sin{\theta_i} + k_y \cos{\theta_i}.
\end{equation}
We include three angles so that the total power spectral density is
\begin{equation}
f(k_x,k_y) = \sum_{i=1}^{i=3} f_i(k_{x,i}'(\theta_i),k_{y,i}'(\theta_i),a_i,b,c).
\end{equation}

This model has 8 free parameters: three angles ($\theta_i$, three amplitudes ($a_i$), a joint parallel exponential constant ($b$) and joint Lorentzian width ($c$).
We only fit the region of the power spectral density above frequencies of 0.05 px$^{-1}$ to focus on the high frequency component of the flat field where the crosshatch is most prevalent.
For the F300M filter and ALONG detector, we find 
for $\theta_1 = 0.9013 \pm 0.0004 \degree, \theta_2 = 68.6041 \pm 0.0007 \degree, \theta_3 = 113.0741 \pm 0.0007, a_1 = 6.9 \pm 0.2 \times 10^6, a_2 = 4.0 \pm 0.1 \times 10^6, a_3 = 4.4 \pm 0.1 \times 10^6, b=666 \pm 1 $ px and $c=4.9933 \pm 0.0004$ px.
The uncertainties were simply derived from the diagonals of the covariance matrix and likely are underestimated.

We take this model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
We then assign random phases uniformly from 0 to 2$\pi$ for the complex Fourier plane because the original image's complex phase distribution is similar to uniform.
Finally, we take the real part of the inverse Fourier transform to create an oversampled image, as shown in \ref{fig:crossHatchSimPSF}.
For comparison to the original flat in Figure \ref{fig:crossHatchA5}, we binned to the oversampled flat field to the native LW pixel resolution of $\sim$0.063 \arcsec.
This simulated pixel flat field with dimensions of 26 by 26 LW pixels has a peak of 1.15 to trough of 0.90 with a robust standard deviation of 0.05.
For comparison, the middle of the original F300M flat for the ALONG detector has a robust standard deviation 0.06.

>>>>

\subsubsection{Crosshatch Modeling}
We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
We divide the 2D Fourier power spectral density by the number of pixels in an input image.
This was experimentally determined to give a power spectral density that does not change with the dimensions of the input image.

We model the two dimensional Fourier power spectral density $f(k_{x,i}',k_{y,i}')$ for one angle $\theta_i$ as
\begin{equation}
f(k_{x,i}',k_{y,i}', a_i, b,c) = a_i \exp{\left(- |k_{x,i}'| / b \right)} \left( \frac{1}{(0.5 c)^2 + k_y'^2} \right),
\end{equation}
where $k_x'$ and $k_y'$ are rotated frequency coordinates in the parallel and perpendicular directions, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorentzian full width at half maximum of the perpendicular dependence.
For each of the three angles, there is a set of rotated coordinates centered at $(k_{x,0},k_{y,0})$= (0,0) following:
\begin{equation}
k_x'(\theta_i) = k_x \cos{\theta_i} + k_y \sin{\theta_i}
\end{equation}
and
\begin{equation}
k_y'(\theta_i) = -k_x  \sin{\theta_i} + k_y \cos{\theta_i}.
\end{equation}
We include three angles so that the total power spectral density is
\begin{equation}
f(k_x,k_y) = \sum_{i=1}^{i=3} f_i(k_{x,i}'(\theta_i),k_{y,i}'(\theta_i),a_i,b,c).
\end{equation}

This model has 8 free parameters: three angles ($\theta_i$, three amplitudes ($a_i$), a joint parallel exponential constant ($b$) and joint Lorentzian width ($c$).
We only fit the region of the power spectral density above frequencies of 0.05 px$^{-1}$ to focus on the high frequency component of the flat field where the crosshatch is most prevalent.
For the F300M filter and ALONG detector, we find 
for $\theta_1 = 0.9013 \pm 0.0004 \degree, \theta_2 = 68.6041 \pm 0.0007 \degree, \theta_3 = 113.0741 \pm 0.0007, a_1 = 3.93 \pm 0.01 \times 10^{-7}, a_2 = 2.305 \pm 0.007 \times 10^{-7}, a_3 = 2.540 \pm 0.007 \times 10^{-7}, b=0.3243 \pm 0.0007 $ px$^{-1}$ and $c=2.44 \pm 0.03 \times 10^{-2}$ px$^{-1}$.
The uncertainties were simply derived from the diagonals of the covariance matrix and likely are underestimated.

@@

We take the exponential model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
We then assign random phases uniformly from 0 to 2$\pi$ for the complex Fourier plane because the original image's complex phase distribution is similar to uniform.
Finally, we take the real part of the inverse Fourier transform to create an oversampled image, as shown in \ref{fig:crossHatchSimPSF}.
For comparison to the original flat in Figure \ref{fig:crossHatchA5}, we binned to the oversampled flat field to the native LW pixel resolution of $\sim$0.063 \arcsec.
This simulated pixel flat field with dimensions of 26 by 26 LW pixels has a peak of 1.15 to trough of 0.90 with a robust standard deviation of 0.05.
For comparison, the middle of the original F300M flat for the ALONG detector has a robust standard deviation 0.06.
